### 2015-08-08 ThesisJo/derivations.tex
la2pdf commit - 2015:08:08	09:50:29	(Sat 8.Aug)
la2pdf commit - 2015:08:08	10:20:34	(Sat 8.Aug)
la2pdf commit - 2015:08:08	10:56:32	(Sat 8.Aug)
la2pdf commit - 2015:08:08	11:26:45	(Sat 8.Aug)
la2pdf commit - 2015:08:08	14:11:37	(Sat 8.Aug)

>>>>

\newpage
\section{Window Parameters}

Signal model, monochromatic place wave from broadside with gaussian noise:
\begin{align}
x_m[n] = s_m[n] + q[n] = Ae^{j\Omega_0mn} + q[n]
\end{align}

Beamformer output
\begin{align}
z[n] = \sumb{n}{} w^*[n]\;x[n]
\end{align}

Frequency response of the window

\begin{align}
W(k_x) = \sumb{m}{} w_m\;e^{jk_x \p_x} =
\begin{cases}
\frac{\sin\left(\frac{M}{2}k_x d\right)}{\sin\left(\frac{1}{2}k_x d\right)} & \text{rectangular}                                         
\end{cases}
\end{align}

Applying a window reduces the signal power because it gets attenuated at both ends. We quantify this effect with the coherent power gain:

\begin{align}
W(\k) &= \sumb{m}{} w_m\;e^{j\k\cdot\p_m}
\end{align}

\begin{align}
Z(\k) &= \sumb{m}{} w_m\;(s_m+q_m)\;e^{-j\k\cdot\p_m} \nn
&= \sumb{m}{} w_m\;A\;e^{j\k\cdot\p_m}\;e^{-j\k\cdot\p_m} + \sumb{m}{} w_m\;q_m\;e^{j\k\cdot\p_m} \nn
&= A \underbrace{\sumb{m}{} w_m}_\text{signal gain} + \sumb{m}{} w_m\;q_m\;e^{j\k\cdot\p_m}
\end{align}

Worst Case Processing Loss = Prosessing Loss + Scallopping Loss

=> a measure of the worst case reduction in SNR which results from the combination of the window function and the worst case frequency location.
